\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing income inequality with tax data - Switzerland from 1917 to 2010}

### 2014-12-16 paper/subdocuments/results.Rnw
indexed fig_measures to 1945/1946

estv_masse <- estv %>% 
  filter(kanton=="CH",
         eink_art=="Nach steuerbarem Einkommen",
         fall=="Normalfälle",
         anz_pflichtige>0) %>%
        # steuerperiode!=1945.5) %>% 
  select(bemessungsjahre, steink, kanton, eink_ll, eink_ul,anz_pflichtige) %>%
  group_by(factor(bemessungsjahre)) %>%
  mutate(mean_steink=steink/anz_pflichtige) %>%
  summarise(Gini=gini(mean_steink,weights=anz_pflichtige),Atkinson=getAtkinson(mean_steink,w=anz_pflichtige),Theil=getTheil(mean_steink,w=anz_pflichtige))
estv_masse$id<-1
names(estv_masse)<-c("Year","Gini","Atkinson","Theil","id")
try(detach("package:reshape", unload=TRUE))
library(reshape2)
estv_masse_long <- melt(estv_masse,id=c("id","Year"))

>>>>

estv_masse <- estv %>% 
  filter(kanton=="CH",
         eink_art=="Nach steuerbarem Einkommen",
         fall=="Normalfälle",
         anz_pflichtige>0) %>%
        # steuerperiode!=1945.5) %>% 
  select(bemessungsjahre, steink, kanton, eink_ll, eink_ul,anz_pflichtige) %>%
  group_by(factor(bemessungsjahre)) %>%
  mutate(mean_steink=steink/anz_pflichtige) %>%
  summarise(Gini=gini(mean_steink,weights=anz_pflichtige),Atkinson=getAtkinson(mean_steink,w=anz_pflichtige),Theil=getTheil(mean_steink,w=anz_pflichtige))
estv_masse$id<-1
estv_masse<-estv_masse[as.numeric(estv_masse$Year)>4,]

names(estv_masse)<-c("Year","Gini","Atkinson","Theil","id")
try(detach("package:reshape", unload=TRUE))
library(reshape2)
estv_masse_long <- melt(estv_masse,id=c("id","Year"))
